Phase Curves of WASP-103b

### 2017-10-01 ms.tex
intro

\section{Introduction} \label{sec:intro}
It is a truism to say that planets are three-dimensional objects, but worth exploring the specific challenges. Short period, tidally locked planets are intensely irradiated on the day side, which can lead to dramatic

The challenge is to reveal this structure at great distances, when we cannot spatially resolve the photosphere of the planet.

Phase curves!

@@

\section{Light Curve Fits}
which orbits/data

>>>>

\section{Introduction} \label{sec:intro}
It is a truism to say that planets are round.  The. And yet planets' roundness gives rise to a host of complications:  atmospheric circulation, variable , gradients in chemistry, cloud formation and evaporation, and time-dependent phenomena (weather).

It is a challenge is to reveal this structure at great distances, when we cannot spatially resolve the photosphere of the planet.  Most observations of exoplanet atmospheres are sensitive to a single isolated region  -- either the terminator, for transmission spectroscopy, or the disk-integrated dayside, for emission spectroscopy.  The solution to this problem is to observe phase curves of tidally-locked planets, which monitor the brightness of the planet over its entire orbit. As the orbital phase changes, the observer

The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson??}, and was followed by FIXME more (with IRAC). Several trends emerged from these measurements, including eastward shifted hotspots (which suggest super-rotating equatorial jets), larger day-night temperature contrast for shorter period planets (ref), . The first spectroscopic phase curve was measured with Hubble's Wide Field Camera 3 (WFC3) by \citep{stevenson???} for the hot Jupiter WASP-43b. Found low albedo, offset hotspot, water visible at other phases,

In parallel with these observations, there have been major advances in the theory of exoplanet atmospheres in three-dimensions. Global circulation models (GCMs) are now capable of self-consistent radiative transfer and atmospheric dynamics (refs) and are beginning to include clouds (refs?).

In addition to GCMs, work on the inverse problem Cowan - how to get maps, . SPIDERMAN, an open-source Python package designed to take any temperature or brightness map of a planet and output the corresponding phase curve, so that we can readily connect GCMs to phase curve observations.

In this paper we present \HST\ and \Spitzer\ phase curve observations of WASP-103b, a hot Jupiter with a mass of X, radius of Y, period of Z (cite discovery paper). These properties are similar to WASP-43b, except that WASP-103b has a much (FIXME vs FIXME K) thanks to its hot F?? star host. By comparing the phase curves of these two planets, we can test the effect of irradiation on the climate of the planet.

The structure of the paper is as follows:

@@

\subsection{Photometric Monitoring}

\section{Light Curve Fits}
which orbits/data
ellipsoidal variations/doppler beaming
